Response to reviewers

### 2022-02-08 paper/paper.Rmd
reconciling the statistical value chain with wild and textbook data terms

@LooMarkvander2018Sdcw describe the notion of a "statistical value chain" where the production stages of the data cleaning process are earmarked as raw data (data as arrived to the desk of an analyst), input data (data organised with correct type and identified variables) and valid data (data that faithfully represent the variables).  In this section, we outline the steps to download the raw data (Section \@ref(getdata)) and then tidy the raw data into input data, specifically for the demographic variables (Section \@ref(tidydemog)) and the employment variables (Section \@ref(tidyemp)), so that the resulting input data can be used downstream for validating the data as described in Section \@ref(ida).

>>>>

@LooMarkvander2018Sdcw in the context of official statistics describe the "statistical value chain" which includes various production stages of the data cleaning process as raw data (data in the initial that it arrives), input data (data organised with correct type and identified variables) and valid data (data that has been cleaned and more accurately represents the intent of variables). What we have colorfully named as wild data can be considered to be raw data, and valid data could be considered to be textbook data, in the above statistical value chain. In this section, we outline the steps to download the raw data (Section \@ref(getdata)) and then tidy the raw data into input data, specifically for the demographic variables (Section \@ref(tidydemog)) and the employment variables (Section \@ref(tidyemp)), so that the resulting input data can be used downstream for validating the data as described in Section \@ref(ida).

### 2022-02-08 paper/paper.tex
reconciling the statistical value chain with wild and textbook data terms

M. van der Loo and de Jonge (2018) describe the notion of a ``statistical value chain'' where the production stages of the data cleaning process are earmarked as raw data (data as arrived to the desk of an analyst), input data (data organised with correct type and identified variables) and valid data (data that faithfully represent the variables). In this section, we outline the steps to download the raw data (Section \ref{getdata}) and then tidy the raw data into input data, specifically for the demographic variables (Section \ref{tidydemog}) and the employment variables (Section \ref{tidyemp}), so that the resulting input data can be used downstream for validating the data as described in Section \ref{ida}.

>>>>

M. van der Loo and de Jonge (2018) in the context of official statistics describe the ``statistical value chain'' which includes various production stages of the data cleaning process as raw data (data in the initial that it arrives), input data (data organised with correct type and identified variables) and valid data (data that has been cleaned and more accurately represents the intent of variables). What we have colorfully named as wild data can be considered to be raw data, and valid data could be considered to be textbook data, in the above statistical value chain. In this section, we outline the steps to download the raw data (Section \ref{getdata}) and then tidy the raw data into input data, specifically for the demographic variables (Section \ref{tidydemog}) and the employment variables (Section \ref{tidyemp}), so that the resulting input data can be used downstream for validating the data as described in Section \ref{ida}.

### 2022-02-08 response/response1.Rmd
reconciling the statistical value chain with wild and textbook data terms

Yes, there is grey area in these three activities. Thanks for pointing out Chatfield's original viewpoint, which differs from Huebner et al's. We have revised this paragraph to de-emphasize cleaning as being part of IDA. We have kept the explanation of the terminology of IDA and EDA because we think this is important for clarifying for teaching purposes.

@@

Outlier detection

@@

* We have fixed the sentences and the reference.

>>>>

Yes, there is grey area in these three activities. Thanks for pointing out Chatfield's original viewpoint, which differs from Huebner et al's. We have revised this paragraph to de-emphasize cleaning as being part of IDA. We have kept the explanation of the terminology of IDA and EDA because we think this is important to clarify for teaching purposes.

@@

XXX We need to review this literature. It's not true that we have ignored it, the main reference is Dasu! But we need to decide whether there is more that we shoudl cite.

Outlier detection ???

@@

* We have fixed the sentences and the reference. XXX Which one?
